The force-free magnetosphere of a Kerr black hole: the role of boundary conditions

### 2018-06-27 paper/ms.tex
save

In Figure \ref{fig:omega}, we show the angular velocity function $\Omega(A_\phi)$ for different BH spins and
compare it with the counterpart obtained from recent high-resolution simulations done by East and Yang \cite{East2018}.
For reference, we also plot the leading-order analytic solution in the slow-rotation limit \cite{Pan2014, East2018},
\be
    \Omega = \WH\frac{\sqrt{1-\psi}} {1+\sqrt{1-\psi}},
\ee
where $\psi = \Ap/(2B_0M^2)$.
From our solutions, we find the magnetic flux entering the ergosphere $\AEE$ increases with BH spin and approach
$2.75 B_0 M^2$ for extremal spins (upper panel of Figure \ref{fig:omega}),
which is about $\sim 5\%$ lower than the simulation result, while the angular velocity $\Omega$ as a function
of normalized magnetic flux $\Ap/\AEE$ shows a good agreement with the simulation results.

@@

\begin{figure}
\includegraphics[scale=0.6]{f2a}
\includegraphics[scale=0.6]{f2b}
\caption{\label{fig:omega} Upper panel: the angular velocity functions $\Omega(\Ap)$ for different BH spins.
Lower Panel: comparison of our numerical results (solid lines) with the simulation results in \cite{East2018} (dashed lines).}
\end{figure}

\begin{figure}
\includegraphics[scale=0.6]{f3}
\caption{\label{fig:Edot} Comparison of the energy extraction rate $\dot E(\WH)$ obtained from our
numerical solutions and from the high-resolution force-free simulations \cite{East2018},
where the former is lower than the latter by $\sim 10\%$ for large spins.}
\end{figure}

@@

In Figure \ref{fig:Edot}, we compare the energy extraction rate $\dot E(\WH)$ derived from our numerical solutions with
East and Yang's simulation results \cite{East2018}, where
the points are taken from either the simulations or our numerical solutions, while the solid lines are
corresponding polynomial fitting curves which require to approach Eq.(\ref{eq:lowEdot}) for small spins and to be flat for extremal spins.
As expected, our energy extraction rate $\dot E$ is $\sim 10\%$ lower than the corresponding simulation results,
due to the $\sim 5\%$ smaller magnetic flux $\AEE$.

@@

\subsection{General application}
In real astrophysics environment, we expect the field configurations are more close to parabolas instead of
being strictly vertical. Due to the same topology, it is reasonable to expect
the marginally force-free boundary
condition (\ref{eq:bc3}) is also a good work approximation. The features we observed the uniform field solution
should also apply here. The numerical method for solving the GS equation and self-consistently imposing the boundary
condition (\ref{eq:bc3}).

\subsection{Near-horizon field lines}
In one of our previous papers \cite{Pan2016a}, we made a claim that ``in the steady axisymmetric force-free magnetosphere
around a Kerr BH, all magnetic field lines that cross the infinite-redshift surface must intersect the event
horizon" based on two
However, simulations shows that there exists an equatorial current sheet within the ergosphere, where
the force-free condition breaks down.

>>>>

In Figure \ref{fig:omega}, we show the angular velocity function $\Omega(A_\phi)$ for different BH spins and
compare it with the counterpart obtained from recent high-resolution simulations done by East and Yang \cite{East2018}.
For reference, we also plot the leading-order analytic solution in the slow-rotation
limit \cite{Beskin2013, Pan2014, Gralla2015, East2018},
\be
    \Omega = \WH\frac{\sqrt{1-\psi}} {1+\sqrt{1-\psi}},
\ee
where $\psi = \Ap/(2B_0M^2)$.
From our numerical solutions, we find the magnetic flux entering the ergosphere $\AEE$ increases with BH spin and approach
$2.75 B_0 M^2$ for extremal spins (upper panel of Figure \ref{fig:omega}),
which is about $\approx 5\%$ lower than the simulation result (Figure 3 of \cite{East2018}),
while the angular velocity $\Omega$ as a function
of normalized magnetic flux $\Ap/\AEE$ shows a good agreement with the simulation results.

@@

\begin{figure}
\includegraphics[scale=0.6]{f2a}
\includegraphics[scale=0.6]{f2b}
\caption{\label{fig:omega} Upper panel: the angular velocity  $\Omega(\Ap)$ for different BH spins.
Lower Panel: comparison of our numerical results (solid lines) with the simulation results of
Ref. \cite{East2018} (dashed lines). For reference, we also plot the leading order analytic solution in
dash-dotted lines.}
\end{figure}

\begin{figure}
\includegraphics[scale=0.6]{f3}
\caption{\label{fig:Edot} Comparison of the energy extraction rates $\dot E(\WH)$ obtained from
three different approaches: the leading-order analytic solution (\ref{eq:lowEdot}),
our numerical solutions and  the high-resolution force-free simulations \cite{East2018}.}
\end{figure}

@@

In Figure \ref{fig:Edot}, we compare the energy extraction rate $\dot E(\WH)$
derived from our numerical solutions with East and Yang's simulation results
\cite{East2018}, where the data points are taken from either the simulations
or our numerical solutions, while the solid lines are corresponding polynomial
fitting curves which we require to approach Eq.(\ref{eq:lowEdot}) for small
spins and to be flat for extremal spins. As expected, our energy extraction
rate $\dot E(\WH)$ is $\approx 10\%$ lower than the corresponding simulation results,
due to the $\approx 5\%$ smaller magnetic flux $\AEE$.

@@

\subsection{Application to general field configurations}
In real astrophysics environment, we expect the field configurations are more close to parabolas instead of
being strictly vertical. Due to the same topology, it is reasonable to expect
the marginally force-free boundary
condition (\ref{eq:bc3}) is also a good work approximation. The features we observed the uniform field solution
should also apply here. The numerical method for solving the GS equation and self-consistently imposing the boundary
condition (\ref{eq:bc3}).

\subsection{Near-horizon field configuration}
In one of our previous papers \cite{Pan2016a}, we made a claim that ``in the steady axisymmetric force-free magnetosphere
around a Kerr BH, all magnetic field lines that cross the infinite-redshift surface must intersect the event
horizon".
However, simulations shows that an equatorial current sheet inevitably forms within the ergosphere , where
the force-free condition breaks down.
